### 2024-03-03 paper.tex
base project

\documentclass[12pt]{article}
\usepackage{times}
\usepackage{blindtext}
\usepackage{url}

\title{Mathematical Observation on the Homelessness Crisis through Mathematical Methods}
\author{Mufaro Machaya, Nam Le, Ben Stillwell \\ Cy-Fair Senior High School \\ Cypress, Texas}
\date{March 3, 2024}

\begin{document}

\newpage

\large{Executive Summary}
\blindtext

\maketitle
\newpage
\tableofcontents

\newpage

\section{Introduction}
Understanding the housing shortage has become more important than ever, as rates of homelessness have reached
unprecedented and potentially dire level\cite{Census2010ACSDP1Y2010.DP04}. Moving into the future, it is
undeniably critical for promoting the general welfare of United States populations to best understand housing for
influencing public policy across major cities in the United States. Thus, we have prepared the following mathematical
models to best understand such a trend.

\newpage

\section{It was the Best of Times}

\subsection{Restatement of the Problem}
The first problem asks us to develop a mathematical model to predict changes to the housing supply over the next 50
years in two cities of our choosing: Seattle, Washington; and Albequerque, New Mexico.

\subsection{Assumptions and Justifications}
\subsection{Model Development}
\subsection{Results}
\subsection{Reflecting on the Model}

\newpage

\section{It was the Worst of Times}

\subsection{Restatement of the Problem}
\subsection{Assumptions and Justifications}
\subsection{Model Development}
\subsection{Results}
\subsection{Reflecting on the Model}

\newpage

\section{Rising from this Abyss}

\subsection{Restatement of the Problem}
\subsection{Assumptions and Justifications}
\subsection{Model Development}
\subsection{Results}
\subsection{Reflecting on the Model}

\newpage

\bibliographystyle{plain}
\bibliography{sources}

\end{document}

### 2024-03-03 paper.tex
now with sample data
1/2 question 1

@@
 \usepackage{url}
+\usepackage{float}
 
-\title{Mathematical Observation on the Homelessness Crisis through Mathematical Methods}
+\title{Observing the United States' Homelessness Crisis through Mathematical Methods}
 \author{Mufaro Machaya, Nam Le, Ben Stillwell \\ Cy-Fair Senior High School \\ Cypress, Texas}
@@
 
-\large{Executive Summary}
+\section*{Executive Summary}
 \blindtext
@@
 Understanding the housing shortage has become more important than ever, as rates of homelessness have reached
-unprecedented and potentially dire level\cite{Census2010ACSDP1Y2010.DP04}. Moving into the future, it is
+unprecedented and potentially dire level\cite{NPR-ABGC-2022}. Moving into the future, it is
 undeniably critical for promoting the general welfare of United States populations to best understand housing for
@@
 \subsection{Assumptions and Justifications}
+
+\textit{There will be no immense, drastic, and long-term permanent changes to housing production possibility
+within the next fifty years.} \\
+
+\noindent
+Justification: Events that will drastically change the ability to produce housing, such as immense wars or widespread
+natural disasters, are neigh-impossible to detect accurately with a simple mathematical model. The only events that can
+be accurately tracked through mathematical means over short periods of time are cyclical events, like economic
+recessions or inflation. \\
+
+\noindent
+\textit{Occupied housing will not be considered part of the available total housing supply.} \\
+
+\noindent
+Justification: In regards to fixing the homelessness crisis, housing that can be considered available for allocation to
+unhoused people inherently must be unoccupied by others. \\
+
+\noindent
+\textit{Differences in median housing costs and median income per capita across regions in both Albequerque and Seattle
+will not be considered in determining housing availability.} \\
+
+\noindent
+Justification: These factors hold a strong correlation with housing unavailability, yet we assume them to have no
+causal relationship. \\
+
+\noindent
+\textit{The National GDP will have a strong-enough correlation with housing availability to aid in accurately
+accounting for cyclical economic trends.} \\
+
+\noindent
+Justification: We fully recognize that national economic health will not be inherently causal with housing availability
+in select cities, but on a macroeconomic scale, the strength of the economy will be reasonably provide a benchmark for
+predicting the economic decisions of housing construction companies and consumers.
+This relies on the assumption that in times of economic prosperity,
+
 \subsection{Model Development}
+For our housing availability model, we choose to use a simple vector machine that regresses historical housing availiability
+data for both Albequerque and Seattle, and from there, we cross-reference this data with historical economic trends
+across the United States to best model housing availability over time given cyclical economic trends.
+
+\noindent
+To begin, we trained the model on the following datasets for housing availability in Albequerque and Seattle and the
+national GDP of the United States.
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c c c|} 
+    \hline 
+    Year & Total housing units & Occupied units & Vacant units \\ [0.5ex]
+    \hline
+    2010  &  234,891 & 217,256 & 17,635 \\
+    2011  &  237,735 & 220,060 & 17,675 \\
+    2012  &  239,718 & 222,584 & 17,134 \\
+    2013  &  240,277 & 222,491 & 17,786 \\
+    2014  &  240,961 & 222,868 & 18,093 \\
+    2015  &  241,326 & 222,098 & 19,228 \\
+    2016  &  242,070 & 221,320 & 20,750 \\
+    2017  &  243,402 & 221,119 & 22,283 \\
+    2018  &  244,382 & 222,748 & 21,634 \\
+    2019  &  245,476 & 224,166 & 21,310 \\
+    2020  &  247,926 & 229,701 & 18,225 \\
+    2021  &  252,924 & 236,191 & 16,733 \\
+    2022  &  255,178 & 239,800 & 15,378 \\ [1ex] 
+    \hline
+  \end{tabular}
+  \caption{Housing Statistics in Albequerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c c c|}
+    \hline
+    Year & Total housing units & Occupied units & Vacant units \\ [0.5ex]
+    \hline
+    2010 & 302,465 & 280,453 & 22,012 \\
+    2011 & 304,164 & 282,480 & 21,684 \\
+    2012 & 306,694 & 285,476 & 21,218 \\
+    2013 & 309,205 & 288,439 & 20,766 \\
+    2014 & 311,286 & 290,822 & 20,464 \\
+    2015 & 315,950 & 296,633 & 19,317 \\
+    2016 & 322,795 & 304,157 & 18,638 \\
+    2017 & 334,739 & 314,850 & 19,889 \\
+    2018 & 344,503 & 323,446 & 21,057 \\
+    2019 & 354,475 & 331,836 & 22,639 \\
+    2020 & 367,337 & 344,629 & 22,708 \\
+    2021 & 362,809 & 337,361 & 25,448 \\
+    2022 & 372,436 & 345,246 & 27,190 \\ [1ex]
+    \hline
+  \end{tabular}
+  \caption{Housing Statistics in Seattle, Washington \cite{Census2010ACSDP5Y2010.DP04}}
+\end{table}
+
+\iffalse
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c|l|c|l|}
+    \hline
+    Year & GDP & Year & GDP \\ [0.5ex]
+    \hline
+    1980 & 2857.3085 & 2005 & 13039.197 \\
+    1981 & 3207.04125 & 2006 & 13815.583 \\
+    1982 & 3343.78925 & 2007 & 14474.227 \\
+    1983 & 3634.0365 &  2008 & 14769.86175 \\
+    1984 & 4037.614 & 2009 & 14478.06725 \\
+    1985 & 4338.9805 & 2010 & 15048.971 \\
+    1986 & 4579.6325 & 2011 & 15599.7315 \\
+    1987 & 4855.21625 & 2012 & 16253.97 \\
+    1988 & 5236.438 & 2013 & 16880.68325 \\
+    1989 & 5641.5795 & 2014 & 17608.13825 \\
+    1990 & 5963.1445 & 2015 & 18295.019 \\
+    1991 & 6158.12925 & 2016 & 18804.91325 \\
+    1992 & 6520.32725 & 2017 & 19612.1025 \\
+    1993 & 6858.5585 & 2018 & 20656.5155 \\
+    1994 & 7287.2365 & 2019 & 21521.395 \\
+    1995 & 7639.74925 & 2020 & 21322.9495 \\
+    1996 & 8073.12175 & 2021 & 23594.03075 \\
+    1997 & 8577.5525 & 2022 & 25744.10825 \\
+    1998 & 9062.81675 & 2023 & 27357.842 \\
+    1999 & 9631.17175 & \\ 
+    2000 & 10250.952 & \\
+    2001 & 10581.929 & \\
+    2002 & 10929.10825 & \\
+    2003 & 11456.4495 & \\
+    2004 & 12217.19575 & \\ [1ex]
+    \hline
+  \end{tabular}
+  \caption{Gross Domestic Product of the United States in Billions of Dollars, Adjusted for Inflation \cite{FREDGDP}}
+\end{table}
+\fi
+
+\noindent
+Due to the limited size of the dataset, we chose to use a $C$ value for our SVM closer to 1.0 to prevent overfitting or
+underfitting of the data.
+
 \subsection{Results}
+
 \subsection{Reflecting on the Model}
@@
 
+\Urlmuskip=0mu plus 1mu\relax
 \bibliographystyle{plain}

### 2024-03-03 model.py

@@ -1,0 +1,4 @@
+import numpy as np
+from sklearn.nvm import LinearSVR
+
+

### 2024-03-04 paper.tex
part 1 complete

@@
 \usepackage{float}
+
+\usepackage{graphicx}
+\graphicspath{{./figures/}}
 
@@
 
-\noindent
-\textit{The National GDP will have a strong-enough correlation with housing availability to aid in accurately
-accounting for cyclical economic trends.} \\
-
-\noindent
-Justification: We fully recognize that national economic health will not be inherently causal with housing availability
-in select cities, but on a macroeconomic scale, the strength of the economy will be reasonably provide a benchmark for
-predicting the economic decisions of housing construction companies and consumers.
-This relies on the assumption that in times of economic prosperity,
-
 \subsection{Model Development}
@@
   \end{tabular}
-  \caption{Housing Statistics in Albequerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}}
+  \caption{Housing Statistics in Albequerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}.}
 \end{table}
@@
   \end{tabular}
-  \caption{Housing Statistics in Seattle, Washington \cite{Census2010ACSDP5Y2010.DP04}}
+  \caption{Housing Statistics in Seattle, Washington \cite{Census2010ACSDP5Y2010.DP04}.}
 \end{table}
-
-\iffalse
-\begin{table}[H]
-  \centering
-  \begin{tabular}{|c|l|c|l|}
-    \hline
-    Year & GDP & Year & GDP \\ [0.5ex]
-    \hline
-    1980 & 2857.3085 & 2005 & 13039.197 \\
-    1981 & 3207.04125 & 2006 & 13815.583 \\
-    1982 & 3343.78925 & 2007 & 14474.227 \\
-    1983 & 3634.0365 &  2008 & 14769.86175 \\
-    1984 & 4037.614 & 2009 & 14478.06725 \\
-    1985 & 4338.9805 & 2010 & 15048.971 \\
-    1986 & 4579.6325 & 2011 & 15599.7315 \\
-    1987 & 4855.21625 & 2012 & 16253.97 \\
-    1988 & 5236.438 & 2013 & 16880.68325 \\
-    1989 & 5641.5795 & 2014 & 17608.13825 \\
-    1990 & 5963.1445 & 2015 & 18295.019 \\
-    1991 & 6158.12925 & 2016 & 18804.91325 \\
-    1992 & 6520.32725 & 2017 & 19612.1025 \\
-    1993 & 6858.5585 & 2018 & 20656.5155 \\
-    1994 & 7287.2365 & 2019 & 21521.395 \\
-    1995 & 7639.74925 & 2020 & 21322.9495 \\
-    1996 & 8073.12175 & 2021 & 23594.03075 \\
-    1997 & 8577.5525 & 2022 & 25744.10825 \\
-    1998 & 9062.81675 & 2023 & 27357.842 \\
-    1999 & 9631.17175 & \\ 
-    2000 & 10250.952 & \\
-    2001 & 10581.929 & \\
-    2002 & 10929.10825 & \\
-    2003 & 11456.4495 & \\
-    2004 & 12217.19575 & \\ [1ex]
-    \hline
-  \end{tabular}
-  \caption{Gross Domestic Product of the United States in Billions of Dollars, Adjusted for Inflation \cite{FREDGDP}}
-\end{table}
-\fi
 
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.9\textwidth]{chart1}
+  \caption{The number of vacancies in Albequerque and Seattle from 2010 to 2022 \cite{Census2010ACSDP1Y2010.DP04,Census2010ACSDP5Y2010.DP04}.}
+\end{figure}
+
+\noindent
+Let $H(x)$ equal the number of available houses for a given year, where $x$ is the current year (absolute from year 0, such as 2024). Simple regression on this dataset results in a total trendline of
+
+$$H_{\textrm{\small TOTAL}}(x) = 385x - 735,364$$
+
+\noindent
+where $R^{2}_{\textrm{\small TOTAL}} = 0.586$, and an average trendline of
+
+$$H_{\textrm{\small AVG}}(x) = 192x - 367,682$$
+
+\noindent
+where $R^{2}_{\textrm{\small AVG}} = 0.586$. \\
+
+\noindent
+A coefficient of determination of $0.586$ is undeniably subpar due to the immense indifficulty in representing vast differences across the trends with linear functions.
+
 \subsection{Results}
 
+With this model, we can predict the following housing statistics for 2034 (10 years in the future), 2044 (20 years in the future), and 2074 (50 years in the future):
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c|c c|}
+    \hline
+    Year & Years from 2024 & Total Available Homes & Average Available Homes in Each City \\
+    \hline
+    2034 & 10 & 47,726 & 22,846 \\
+    2044 & 20 & 51,576 & 24,766 \\
+    2074 & 50 & 63,126 & 30,526 \\
+    \hline
+  \end{tabular}
+\end{table}
+
 \subsection{Reflecting on the Model}
+
+Overall, our model proves generally weak at predicting immense, unforseen changes to the economic situation of both cities such as the advent of war, the outbreak of a major epidemic/pandemic, or a large-scale natural disaster.
+This model is best for serving as a general, aggregate predictor of housing availability based on cyclical economic trends.
+Our coefficient of determination $R^{2}$ is certainly low, indicating a lack of accuracy, but this is certainly due to the difficulty of modeling previously-mentioned large-scale events with a linear model.
+\\
+
+\noindent
+Altogether, we can conclude that this model's impact serves best as a general guideline for understanding realistic public policy because it is solely based largely on aggregate, cyclical economic factors that can be reasonably relied upon to occur continuously.
 

### 2024-03-04 paper.tex
fixed bens name
prob 2

@@
 \title{Observing the United States' Homelessness Crisis through Mathematical Methods}
-\author{Mufaro Machaya, Nam Le, Ben Stillwell \\ Cy-Fair Senior High School \\ Cypress, Texas}
+\author{Mufaro Machaya, Nam Le, Ben Stilwell \\ Cy-Fair Senior High School \\ Cypress, Texas}
 \date{March 3, 2024}
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{chart1}
+  \includegraphics[width=0.9\textwidth]{vacancy}
   \caption{The number of vacancies in Albequerque and Seattle from 2010 to 2022 \cite{Census2010ACSDP1Y2010.DP04,Census2010ACSDP5Y2010.DP04}.}
@@
   \centering
-  \begin{tabular}{|c c|c c|}
+  \begin{tabular}{|c c|c c c|}
     \hline 
-    Year & Years from 2024 & Total Available Homes & Average Available Homes in Each City \\
+    &&&&\\
+    Year & \shortstack{Years from 2024} & \shortstack{Total Available \\ Homes} & \shortstack{Average Available \\ Homes in Each \\ City} & \shortstack{Change from 2024} \\
     \hline
-    2034 & 10 & 47,726 & 22,846 \\
-    2044 & 20 & 51,576 & 24,766 \\
-    2074 & 50 & 63,126 & 30,526 \\
+    2024 & 0  & 43,876 & 20,926 & 0 \\
+    2034 & 10 & 47,726 & 22,846 & 1,920 \\
+    2044 & 20 & 51,576 & 24,766 & 1,920 \\
+    2074 & 50 & 63,126 & 30,526 & 1,920 \\
     \hline
@@
 \subsection{Restatement of the Problem}
+The first problem asks us to develop a mathematical model to predict changes to the homeless population over the next 50
+years in two cities of our choosing: Seattle, Washington; and Albequerque, New Mexico.
+
 \subsection{Assumptions and Justifications}
+\textit{Public policy regarding homelessness will stay roughly the same throughout the next fifty years.} \\
+
+\noindent
+Justification: We assume that there will be no significant changes to government policy that would severely change the homeless population, as these immense changes to public policy require immense predictions of political trends beyond the scope of this study.
+\\
+
 \subsection{Model Development}
+For our model, we used yet another linear support vector machine for simple linear regression at $C=1.0$ as trained on the following data sets:
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c c c|} 
+    \hline 
+    Year & Total housing units & Occupied units & Vacant units \\ [0.5ex]
+    \hline
+    2010 & 234,891 & 217,256 & 17,635 \\
+    2011 & 237,735 & 220,060 & 17,675 \\
+    2012 & 239,718 & 222,584 & 17,134 \\
+    2013 & 240,277 & 222,491 & 17,786 \\
+    2014 & 240,961 & 222,868 & 18,093 \\
+    2015 & 241,326 & 222,098 & 19,228 \\
+    2016 & 242,070 & 221,320 & 20,750 \\
+    2017 & 243,402 & 221,119 & 22,283 \\
+    2018 & 244,382 & 222,748 & 21,634 \\
+    2019 & 245,476 & 224,166 & 21,310 \\
+    2020 & 247,926 & 229,701 & 18,225 \\
+    2021 & 252,924 & 236,191 & 16,733 \\
+    2022 & 255,178 & 239,800 & 15,378 \\ [1ex] 
+    \hline
+  \end{tabular}
+  \caption{Housing Statistics in Albequerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}.}
+\end{table}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{homeless-vs-year-alb}
+  \caption{Total Homeless by Year in Albequerque, New Mexico}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{homeless-prop-vs-year-alb}
+  \caption{Percentage of the Population that is Homeless in Albequerque, New Mexico}
+\end{figure}
+
+\noindent
+Therefore, for Albequerque, let $A_{T}(x)$ be total number of homeless people in Albequerque, where $x$ is the current year (which is absolute from 0, such as 2024).
+
+$$A_{T}(x) = 32,757.7 - 15.54(x)$$
+
+\noindent
+Additionally, let $A_{\%}(x)$ be the percentage of Albequerque's population that is homeless, where $x$ is the current year (which is absolute from 0, such as 2024).
+
+$$A_{\%}(x) = .08124 - 3.9(x) \times 10^{-5}$$
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{homeless-vs-year-seattle}
+  \caption{Total Homeless by Year in Seattle, Washington}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\textwidth]{homeless-prop-vs-year-seattle}
+  \caption{Percentage of the Population that is Homeless in Seattle, Washington}
+\end{figure}
+
+\noindent
+Therefore, for Seattle, let $S_{T}(x)$ be total number of homeless people in Seattle, where $x$ is the current year (which is absolute from 0, such as 2024).
+
+$$S_{T}(x) = 341.625x + 7902$$
+
+\noindent
+Additionally, let $S_{\%}(x)$ be the percentage of Seattle's population that is homeless, where $x$ is the current year (which is absolute from 0, such as 2024).
+
+$$S_{\%}(x) = 0.65 - 2.473(x) \times 10^{-5}$$
+
 \subsection{Results}
+
+With this model, we can predict the following homelessness statistics for 2034 (10 years in the future), 2044 (20 years in the future), and 2074 (50 years in the future):
+
+\subsubsection{Albequerque, New Mexico}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c|c c c|}
+    \hline 
+    Year & \shortstack{Years from 2024} & \shortstack{Homeless Percentage} & \shortstack{Total Homeless} & \shortstack{Change from 2024} \\
+    \hline
+    $2024$ & $0$  & $2.304 \times 10^{-3}$ & $1,304.74$ & $0$ \\
+    $2034$ & $10$ & $1.914 \times 10^{-3}$ & $1,149.34$ & $-155.4$ \\
+    $2044$ & $20$ & $1.524 \times 10^{-3}$ & $993.94$   & $-155.4$ \\
+    $2074$ & $50$ & $3.54  \times 10^{-3}$ & $527.74$   & $-155.4$ \\
+    \hline
+  \end{tabular}
+\end{table}
+
+\subsubsection{Seattle, Washington}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c|c c c|}
+    \hline 
+    Year & \shortstack{Years from 2024} & \shortstack{Homeless Percentage} & \shortstack{Total Homeless} & \shortstack{Change from 2024} \\
+    \hline
+    $2024$ & $0$  & $0.6$   & $699,351$    & $0$ \\
+    $2034$ & $10$ & $0.6$   & $702,767.25$ & $3,416.25$ \\
+    $2044$ & $20$ & $0.6$   & $706,183.5$  & $3,416.5$ \\
+    $2074$ & $50$ & $0.599$ & $716,432.25$ & $10,249$ \\
+    \hline
+  \end{tabular}
+\end{table}
+
 \subsection{Reflecting on the Model}
+
+Reflecting on the Models: Our homeless models for both the city of Seattle and Albuquerque proves a little weak, as the homeless population rate won’t have a linear decrease or increase following the year 2023, but will have its ups and downs.
+Although our data for the graphs are not perfect, it offers a distinct trend between the two cities, since Seattle’s estimated homeless population rate is going up, while Albuquerque’s homeless population rate is going down.
+This gives insight on the effectiveness of Albuquerque’s methods in solving the homeless crisis, and should be explored furthermore.
 

### 2024-03-04 paper.tex
done

@@
 \section*{Executive Summary}
-\blindtext
+For the first part of our paper, we were asked to develop a mathematical model to predict changes to the housing
+supply over the next 50 years in two cities of our choosing, of which we chose Seattle, Washington and Albuquerque,
+New Mexico. To solve this, we developed a linear model through regressing historical housing supply data across both
+cities, and determined that it proves weak at accounting for large unforseen events like war, epidemics, or natural
+disasters while still successfully guiding public policy decisions under the assumption that such instances rarely, if
+ever, occur. \\
+
+\noindent
+For the second part of our paper, we are asked to develop a similar model to track the rate of homelessness across
+both cities. Again, we regressed historical homelessness data to develop a linear model, except in these models, we
+chose to develop models designed for each city rather than one aggregate model due to the completely different
+homelessness situations across each city. \\
+
+\noindent
+Lastly, for the third and final part of our paper, we are asked to develop a model to best aid local governments in
+developing public policy to combat homelessness. We conclude that, based on our results from part 2, public policy
+decisions made by Albuquerque will be the most successful, and as such, we chose to mathematically model the effects
+of their public policy on homelessness populations. From there, we reflected on our model and determined that it, yet
+again, fails to account for difficult-to-foresee situations but serves well as a general guideline for local
+governments when developing public policy decisions.
 
@@
 The first problem asks us to develop a mathematical model to predict changes to the housing supply over the next 50
-years in two cities of our choosing: Seattle, Washington; and Albequerque, New Mexico.
+years in two cities of our choosing: Seattle, Washington; and Albuquerque, New Mexico.
 
@@
 \noindent
-\textit{Differences in median housing costs and median income per capita across regions in both Albequerque and Seattle
+\textit{Differences in median housing costs and median income per capita across regions in both Albuquerque and Seattle
 will not be considered in determining housing availability.} \\
@@
 For our housing availability model, we choose to use a simple vector machine that regresses historical housing availiability
-data for both Albequerque and Seattle, and from there, we cross-reference this data with historical economic trends
+data for both Albuquerque and Seattle, and from there, we cross-reference this data with historical economic trends
 across the United States to best model housing availability over time given cyclical economic trends.
@@
 \noindent
-To begin, we trained the model on the following datasets for housing availability in Albequerque and Seattle and the
+To begin, we trained the model on the following datasets for housing availability in Albuquerque and Seattle and the
 national GDP of the United States.
@@
   \end{tabular}
-  \caption{Housing Statistics in Albequerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}.}
+  \caption{Housing Statistics in Albuquerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}.}
 \end{table}
@@
   \includegraphics[width=0.9\textwidth]{vacancy}
-  \caption{The number of vacancies in Albequerque and Seattle from 2010 to 2022 \cite{Census2010ACSDP1Y2010.DP04,Census2010ACSDP5Y2010.DP04}.}
+  \caption{The number of vacancies in Albuquerque and Seattle from 2010 to 2022 \cite{Census2010ACSDP1Y2010.DP04,Census2010ACSDP5Y2010.DP04}.}
 \end{figure}
@@
 The first problem asks us to develop a mathematical model to predict changes to the homeless population over the next 50
-years in two cities of our choosing: Seattle, Washington; and Albequerque, New Mexico.
+years in two cities of our choosing: Seattle, Washington; and Albuquerque, New Mexico.
 
@@
   \centering
-  \begin{tabular}{|c c c c|} 
+  \begin{tabular}{|c c c|} 
     \hline 
-    Year & Total housing units & Occupied units & Vacant units \\ [0.5ex]
+    Year & Total Population & Total Homeless \\ [0.5ex]
     \hline
-    2010 & 234,891 & 217,256 & 17,635 \\
-    2011 & 237,735 & 220,060 & 17,675 \\
-    2012 & 239,718 & 222,584 & 17,134 \\
-    2013 & 240,277 & 222,491 & 17,786 \\
-    2014 & 240,961 & 222,868 & 18,093 \\
-    2015 & 241,326 & 222,098 & 19,228 \\
-    2016 & 242,070 & 221,320 & 20,750 \\
-    2017 & 243,402 & 221,119 & 22,283 \\
-    2018 & 244,382 & 222,748 & 21,634 \\
-    2019 & 245,476 & 224,166 & 21,310 \\
-    2020 & 247,926 & 229,701 & 18,225 \\
-    2021 & 252,924 & 236,191 & 16,733 \\
-    2022 & 255,178 & 239,800 & 15,378 \\ [1ex] 
+    2007 & -       & 1,276 \\
+    2008 & -       & 1,276 \\
+    2009 & -       & 2,002 \\
+    2010 & 531,403 & 2,002 \\
+    2011 & 539,000 & 1,639 \\
+    2012 & 545,083 & 1,431 \\
+    2013 & 549,812 & 1,171 \\
+    2014 & 553,576 & 1,254 \\
+    2015 & 556,092 & 1,287 \\
+    2016 & 556,859 & 1,222 \\
+    2017 & 556,718 & 1,318 \\
+    2018 & 559,202 & 1,340 \\
+    2019 & 559,374 & 1,524 \\
+    2020 & 560,447 & 1,586 \\
+    2021 & 562,336 & 1,567 \\
+    2022 & 562,551 & 1,277 \\
     \hline
   \end{tabular}
-  \caption{Housing Statistics in Albequerque, New Mexico \cite{Census2010ACSDP1Y2010.DP04}.}
+  \caption{Total Population by Year in Albuquerque \cite{Census2022ACSST1Y2022.S0101,HOMELESS-STATS}.}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c|} 
+    \hline 
+    Year & Total Homeless \\ [0.5ex]
+    \hline
+
+    \hline
+  \end{tabular}
+  \caption{}
 \end{table}
@@
   \includegraphics[width=0.8\textwidth]{homeless-vs-year-alb}
-  \caption{Total Homeless by Year in Albequerque, New Mexico}
+  \caption{Total Homeless by Year in Albuquerque, New Mexico}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{homeless-prop-vs-year-alb}
-  \caption{Percentage of the Population that is Homeless in Albequerque, New Mexico}
+  \caption{Percentage of the Population that is Homeless in Albuquerque, New Mexico}
 \end{figure}
@@
 \noindent
-Therefore, for Albequerque, let $A_{T}(x)$ be total number of homeless people in Albequerque, where $x$ is the current year (which is absolute from 0, such as 2024).
+Therefore, for Albuquerque, let $A_{T}(x)$ be total number of homeless people in Albequerque, where $x$ is the current year (which is absolute from 0, such as 2024).
 
@@
 \noindent
-Additionally, let $A_{\%}(x)$ be the percentage of Albequerque's population that is homeless, where $x$ is the current year (which is absolute from 0, such as 2024).
+Additionally, let $A_{\%}(x)$ be the percentage of Albuquerque's population that is homeless, where $x$ is the current year (which is absolute from 0, such as 2024).
 
 $$A_{\%}(x) = .08124 - 3.9(x) \times 10^{-5}$$
+
+\begin{table}[H]
+  \centering
+  \begin{tabular}{|c c c|} 
+    \hline 
+    Year & Total Population & Total Homeless \\ [0.5ex]
+    \hline
+    2007 & -       & 7,902 \\
+    2008 & -       & 8,501 \\
+    2009 & -       & 8,952 \\
+    2010 & 595,240 & 9,022 \\
+    2011 & 603,174 & 8,972 \\
+    2012 & 612,916 & 8,899 \\
+    2013 & 624,681 & 9,106 \\
+    2014 & 637,850 & 8,949 \\
+    2015 & 653,017 & 10,122 \\
+    2016 & 668,849 & 10,730 \\
+    2017 & 688,245 & 11,643 \\
+    2018 & 708,823 & 12,112 \\
+    2019 & 724,305 & 11,199 \\
+    2020 & 741,251 & 11,751 \\
+    2021 & 726,054 & 5,183 \\
+    2022 & 734,603 & 13,368 \\
+    \hline
+  \end{tabular}
+  \caption{Total Population by Year in Seattle \cite{Census2022ACSST1Y2022.S0101,HOMELESS-STATS}.}
+\end{table}
 
@@
 
-\subsubsection{Albequerque, New Mexico}
+\subsubsection{Albuquerque, New Mexico}
 
@@
 \subsection{Restatement of the Problem}
+The third and final question asks us to utilize the results from at least one of our previous models to first develop a final
+model that can be used to best aid a city in combatting the homelessness crisis then analyze the model for its
+strengths and weaknesses given situations like natural disasters, economic recessions, or migrant populations.
+
 \subsection{Assumptions and Justifications}
+\textit{Job availability will be stimulated primarily through public policy from the government.} \\
+
+\noindent
+The intent of this model is to understand how public policy ought to reflect into homelessness statistics without
+heavy consideration to external factors, such as the growth or shrinking of privately funded opportunities
+supplied for homeless people (such as charity or jobs). Such consideration would require more narrow focus on cyclical
+economic trends, when in reference to the success of implementing simple public policy, such methods would be rendered
+unnecessary. For the sake of brevity, lawmakers merely need to understand the general impacts of their legislation rather than their impact in
+context of the entire economic situation of their region.
+
 \subsection{Model Development}
-\subsection{Results}
+
+We developed our model based on the predictions outlined in recent public policy decisions made by Albuquerque city
+officials of combatting homelessness through policy-funded stimulation of job opportunities directly for homeless
+shelter residents\cite{ALB-JOBS}. Given the immense success Albuquerque has had thus far in reducing homelessness year
+after year (as shown in our previous results), we can conclude that their success in providing conncting opportunities
+to the homeless ought to serve as the benchmark for determining public policy for addressing homeless populations
+throughout the nation. \\
+
+\noindent
+Thus, we developed the following model through our previous linear regression processes with data from Albuquerque's
+labor statistics \cite{ALB-LABOR}. Let $N(x)$ equal our homelessness population in Albuquerque for a given year, where $x$ is the
+number of available jobs for the given market.
+
+$$N(x) = 1,368-0.037(x)$$
+
 \subsection{Reflecting on the Model}
+
+This model provides a strong general basis for understanding how the availability of jobs for homeless populations
+within Albequerque serves as an inverse relationship, directly combatting the homelessness crisis in an incredibly
+effective manner. However, we must acknowledge that it is unreliable in consideration to unforseen events that could
+divert resources from providing economic opportunities like jobs for the homeless, such as war or natural disasters,
+due to lacking nuance for accounting for such occurances. Additionally, as a linear model, it will be far less
+accurate for accounting for cyclical movements in the economy, acting as more of an aggregate measure for combatting
+homelessness through job opportunities than a guaranteed predictor of homelessness statistics.
 
